% !TeX spellcheck = en_US
% !TeX root = notes.tex
\section{Ripple}
\begin{itemize}
	\item Ripple is a real-time gross settlement system and currency exchange network
	\item Ripple existed before blockchains, and its main goals are to provide speed, scalability, transparency and stability. With an emphasis on the first two
	\item Ripple required two parties for a transaction to occur
	\begin{itemize}
		\item A regulated financial institution holds funds and issues balances on behalf of customers
		\item Second, market makers, which can be hedge funds or currency traders that provide liquidity in the currency they want to trade in
	\end{itemize}
	\item In Ripple, users make payments in transactions denominated in either fiat transactions or Ripple's internal currency, XRP
	\item When transactions are made in XRP, Ripple can account for the whole transaction history in its internal ledger
	\item For other currencies, Ripple can account for the whole transaction history in its internal ledger
	\item For other currencies, Ripple can only amount for amounts owed (not balances of the users)
	\item Components of the Ripple Network:
	\begin{description}
		\item[Server:] Like a node, runs the Ripple server. Can act as a validator or a spectator
		\item[Unique Node List (UNL):] A list of servers that a server communicates with to form consensus. These servers have to be ``honest''
		\item[Proposer:] A server that broadcasts transactions. Every server tries to include every valid transaction. Only proposals from servers on the UNL are considered
		\item[Ledger:] A record of the amount of currency in each user's account. Each ledger contains:
		\begin{itemize}
			\item A set of transactions
			\item Account Information
			\item Timestamp
			\item Ledger Number
			\item A status bit (to denote whether the ledger is validated or not)
		\end{itemize}
		\item[Consensus and Validating Servers:] Responsible for determining consensus. Verifying proposed changes. Needs to meet escalating consensus
	\end{description}
	\item Ripple has a protection to avoid an attacker spamming XRP transactions, for each XRP transaction, a commission is charged, so attackers will eventually run out of XRP
	\item Biggest blow to Ripple is that while it's distributed, it's not at all decentralized. Ripple owns and runs most of the nodes and maintains a significant percentage of XRP
\end{itemize}