% !TeX spellcheck = en_US
% !TeX root = notes.tex
\section{History of the Web}
\subsection{Origins}
\begin{itemize}
	\item Originated in 1960s -- ARPANet
	\item TCP/IP introduced 1982
	\item DNS developed in 1984
	\item Internet was commercialized in 1995
	\subitem When NSFNET was decommissioned
\end{itemize}

\subsection{WWW}
\begin{itemize}
	\item System of interlinked hypertext documents accessed via Internet
	\item Created by Tim Berners-Lee in 1990 while with CERN
	\subitem HTTP, HTML, web browser, web server
	\subitem WorldWideWeb released 1991 publicly
	\item Mosaic (web browser and Gopher client) 1993
	\item W3C World Wide Web Consortium founded 1994
	\item Commercialization of WWW late 90s
\end{itemize}

\subsection{WaSP}
\begin{itemize}
	\item ``The Web Standards Project'' setup in 1998 by a group of professional web devs and designers
	\item Reforming the W3C recommendations as standards
	\item Push to standardize approaches and implementations across all browsers
\end{itemize}

\subsection{Evolution of WWW}
\begin{description}
	\item[Web 1.0:] static (information retrieval)
	\item[Web 2.0:] collaborative (sharing and production)
	\item[Web 3.0:] semantic and personal (meaningful web)
	\item[Web 4.0:] mobile web
	\item[Web 4.0 \& 5.0:] connections and serendipity
\end{description}

\section{Web Design}
\subsection{What Is It?}
\begin{itemize}
	\item Process of creating the `front-end' of a website
	\item What the users sees and interacts with
	\item Bringing media together into a cohesive whole
	\item Creating a good user experience
\end{itemize}

\subsection{Who's Involved}
\begin{itemize}
	\item Client
	\item Users (indirectly)
	\item Web designer
	\item Web developer
	\item Content editor
\end{itemize}

\subsection{What's Involved}
\subsubsection{Pre-planning and planning}
\begin{itemize}
	\item Client goals, feature requests, target audience
	\item Design documentation
	\item Content gathering/definition
\end{itemize}
\subsubsection{User analysis}
\begin{itemize}
	\item Who are the users?
	\item What will they want/need to do on the site?
	\item Why are they there?
	\item Is your site:
	\subitem Usable
	\subitem Useful
	\subitem Efficient
	\subitem Memorable
	\subitem Enjoyable
	\subitem Aesthetically Pleasing
	\subitem Fun
	\subitem Safe
\end{itemize}
\subsubsection{Information architecture}
\begin{itemize}
	\item How will content be structured on the site?
	\item How will that structure be represented to the user?
\end{itemize}
\subsubsection{Navigation and interaction design}
\begin{itemize}
	\item How will people move around?
	\item How will they know where they are?
	\item What will they be able to do? And how?
\end{itemize}
\subsubsection{Aesthetic and visual design}
\begin{itemize}
	\item What will it look like?
	\item Typography, color, layout
	\item How are elements arranged on the page?
	\item How does it fit with and extend the clients brand?
\end{itemize}
\subsubsection{Prototyping}
\begin{itemize}
	\item Low/high fidelity
	\item Represent aspects of the site
	\item Technological or design based
\end{itemize}
\subsubsection{Evaluation}
\begin{itemize}
	\item User testing
	\item Performance testing
	\item Improve before going live
\end{itemize}
\subsubsection{Accessibility design}
\begin{itemize}
	\item Standards to ensure equal access
	\item Structural, semantic HTML
	\item Allow for different modes of content access
\end{itemize}
\subsubsection{Trust, personalization and globalization}
\begin{itemize}
	\item Engender trust in your site
	\item Build in content personalization/contextualize
	\item Going global and local at the same time
\end{itemize}

\begin{note}{What makes a good website}
	\begin{itemize}
		\item Site purpose and function is clear to the user
		\item Easy to navigate and use
		\item Content is credible, original, useful and timely
		\item Multimedia, where used, is appropriate
		\item Visual design is consistent, appropriate and well organized
		\item Loads quickly and is responsive to user interaction
	\end{itemize}
\end{note}